sensiAnPaper1All

### 2016-01-22 sensiAnPaper1All.Rmd
add predictor resist_start_1_div_2

  #nScenarios <- 100
  nScenarios <- 1000
  ## do model runs
  listOutMix <- sensiAnPaperPart( nScenarios, insecticideUsed = 'mixture' )
  listOutI1 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide1' )
  listOutI2 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide2' )

@@

  #add an extra predictor, the lower starting freq of resistance divided by the larger
  startResistanceRatio <- ifelse( treeInput['P_1',] < treeInput['P_2',], treeInput['P_1',]/treeInput['P_2',], treeInput['P_2',]/treeInput['P_1',])
  treeInput <- rbind(treeInput,startResistanceRatio)

>>>>

  nScenarios <- 10  
  #nScenarios <- 100
  #nScenarios <- 1000
  ## do model runs
  listOutMix <- sensiAnPaperPart( nScenarios, insecticideUsed = 'mixture' )
  listOutI1 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide1' )
  listOutI2 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide2' )

@@

  #add an extra predictor, the lower starting freq of resistance divided by the larger
  resist_start_hi_div_lo <- ifelse( treeInput['P_1',] < treeInput['P_2',], treeInput['P_1',]/treeInput['P_2',], treeInput['P_2',]/treeInput['P_1',])
  treeInput <- rbind(treeInput,resist_start_hi_div_lo)

  #20160122 add test for Ian of resistance1/resistance2
  resist_start_1_div_2 <- treeInput['P_1',]/treeInput['P_2',]
  treeInput <- rbind(treeInput,resist_start_1_div_2)
